\section{The \texttt{Conics\_PH} McStas Component}
Release: McStas 2.7
Date: September 2021

Parabolid-Hyperbolic shells for Wolter optic

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Peter Wilendrup and Erik Knudsen \textless{}br\textgreater{}(derived from Giacomo Resta skeleton-component)
  \item \textbf{Origin:} DTU
  \item \textbf{Date:} September 2021
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
Implements a set of nshells Wolter I Paraboloid/Hyperboloid pairs using conics.h from ConicTracer.

The component has two distinct modes of specifying the geometry:
a) Via the radii vector, parametrized from largest to smallest radius with a length of 'nshells'

b) By specifying radii rmax and rmin, between which a quadratic law distributes 'nshells' surfaces.

The mirrors are assumed to be touching at the mid-optic plane, i.e. there is no gap between primary
and secondary mirror.* By definition the ratio between primary and secondary mirror glancing angles is 1/3.
At present a single m-value is used for all mirrors.
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
rmin & m & Midoptic plane radius of innermost mirror pair. & 0.325 \\
rmax & m & Midoptic plane radius of outermost mirror pair. & 0.615 \\
focal\_length & m & Focal length of the mirror pairs. & 10.070 \\
lp & m & Paraboloid mirror length. & 0.84 \\
lh & m & Hyperboloid mirror length. & 0.84 \\
nshells & 1 & Number of nested shells to expect & 4 \\
m & 1 & Critical angle of mirrors as multiples of Ni. & 1 \\
mirr\_thick & m & Thickness of mirror shell surfaces - NOT YET IMPLEMENTED & 0 \\
disk &   & Flag. If nonzero, insert a disk to block the central area within the innermost mirror. & 1 \\
radii & m & Optional vector of radii (length should match nshells) & NULL \\
R0 & 1 & Reflectivity at Low angles for reflectivity curve approximation & 0.99 \\
Qc & AA-1 & Critical scattering vector & 0.021 \\
W & AA-1 & Width of supermirror cut-off & 0.003 \\
alpha & AA & Slope of reflectivity for reflectivity curve approximation & 6.07 \\
transmit & 1 & Fraction of statistics to assign to transmitted beam - NOT YET IMPLEMENTED & 0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/Conics_PH.comp}{Source code} for \texttt{Conics\_PH.comp}.
\end{itemize}
\IfFileExists{Conics_PH_static.tex}{\input{Conics_PH_static.tex}}{}