\section{The \texttt{Guide\_m} McStas Component}
Release: McStas 1.12c

Neutron guide.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Kristian Nielsen
  \item \textbf{Origin:} Risoe
  \item \textbf{Date:} September 2 1998, Modified 2013
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
Models a rectangular guide tube centered on the Z axis. The entrance lies
in the X-Y plane.
For details on the geometry calculation see the description in the McStas
reference manual.
The reflectivity profile may either use an analytical mode (see Component
Manual) or a 2-columns reflectivity free text file with format
[q(Angs-1) R(0-1)].

Example: Guide(w1=0.1, h1=0.1, w2=0.1, h2=0.1, l=2.0,
R0=0.99, Qc=0.021, alpha=6.07, m=2, W=0.003

%VALIDATION
May 2005: extensive internal test, no bugs found
Validated by: K. Lieutenant

%BUGS
This component does not work with gravitation on. Use component Guide_gravity then.
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
reflect & str & Reflectivity file name. Format [q(Angs-1) R(0-1)] & 0 \\
\textbf{w1} & m & Width at the guide entry &  \\
\textbf{h1} & m & Height at the guide entry &  \\
\textbf{w2} & m & Width at the guide exit &  \\
\textbf{h2} & m & Height at the guide exit &  \\
\textbf{l} & m & Length of guide &  \\
R0\_left & 1 & Low-angle reflectivity, left mirrror. & 0.99 \\
R0\_right & 1 & Low-angle reflectivity, right mirror. & 0.99 \\
R0\_top & 1 & Low-angle reflectivity, top mirror. & 0.99 \\
R0\_bottom & 1 & Low-angle reflectivity, bottom mirror. & 0.99 \\
Qc\_left & AA-1 & Critical scattering vector, left mirrror. & 0.0219 \\
Qc\_right & AA-1 & Critical scattering vector, right mirror. & 0.0219 \\
Qc\_top & AA-1 & Critical scattering vector, top mirror. & 0.0219 \\
Qc\_bottom & AA-1 & Critical scattering vector, bottom mirror. & 0.0219 \\
aleft & AA & Slope of reflectivity, left mirrror. & 6.07 \\
aright & AA & Slope of reflectivity, right mirror. & 6.07 \\
atop & AA & Slope of reflectivity, top mirror. & 6.07 \\
abottom & AA & Slope of reflectivity, bottom mirror. & 6.07 \\
mleft & 1 & m-value of material. Zero means completely absorbing, left mirrror. & 2 \\
mright & 1 & m-value of material. Zero means completely absorbing, right mirror. & 2 \\
mtop & 1 & m-value of material. Zero means completely absorbing, top mirror. & 2 \\
mbottom & 1 & m-value of material. Zero means completely absorbing, bottom mirror. & 2 \\
W\_left & AA-1 & Width of supermirror cut-off, left mirrror. & 0.003 \\
W\_right & AA-1 & Width of supermirror cut-off, right mirror. & 0.003 \\
W\_top & AA-1 & Width of supermirror cut-off, top mirror. & 0.003 \\
W\_bottom & AA-1 & Width of supermirror cut-off, bottom mirror. & 0.003 \\
W & AA-1 & Overall width of supermirror cut-off, overwrites values from individual mirrors & 0 \\
m & 1 & Overall m-value of supermirrors, overwrites values from individual mirrors & 0 \\
alpha & AA & Overall slope of reflectivity, overwrites values from individual mirrors & 0 \\
R0 & 1 & Overall, low-angle reflectivity, overwrites values from individual mirrors & 0 \\
Qc & AA-1 & Overall, critical scattering vector, overwrites values from individual mirrors & 0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/Guide_m.comp}{Source code} for \texttt{Guide\_m.comp}.
\end{itemize}
\IfFileExists{Guide_m_static.tex}{\input{Guide_m_static.tex}}{}