\section{The \texttt{Guide\_honeycomb} McStas Component}
Neutron guide with gravity and honeycomb geometry. Can be channeled and focusing.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} G. Venturi
  \item \textbf{Origin:} \textless{}a href="http://www.ill.fr"\textgreater{}ILL (France)\textless{}/a\textgreater{}.
  \item \textbf{Date:} Apr 2003
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
Models a honeycomb guide tube centered on the Z axis. The entrance lies
in the X-Y plane. Gravitation applies also when reaching the guide input
window. The guide can be channeled (hexagonal channel section; nslit,d parameters).
The guide coating specifications may be entered via different ways (global,
or for each wall m-value).
For details on the geometry calculation see the description in the McStas
reference manual.

Example: Guide_honeycomb(w1=0.1, w2=0.1, l=12,
R0=0.99, Qc=0.0219, alpha=6.07, m=1.0, W=0.003, nslit=1, d=0.0005)
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
\textbf{w1} & m & Width at the guide entry &  \\
w2 & m & Width at the guide exit. If zero, sets w2=w1. & 0 \\
\textbf{l} & m & length of guide &  \\
R0 & 1 & Low-angle reflectivity & 0.995 \\
Qc & AA-1 & Critical scattering vector & 0.0218 \\
alpha & AA & Slope of reflectivity & 4.38 \\
m & 1 & m-value of material. Zero means completely absorbing. & 1.0 \\
W & AA-1 & Width of supermirror cut-off & 0.003 \\
nslit & 1 & Number of horizontal channels in the guide (\textgreater{}= 1) [1] & 1 \\
d & m & Thickness of subdividing walls [0] & 0.0005 \\
mleftup & 1 & m-value of material for leftup.    oblique mirror & -1 \\
mrightup & 1 & m-value of material for rightdown. oblique mirror & -1 \\
mleftdown & 1 & m-value of material for rightdown. oblique mirror & -1 \\
mrightdown & 1 & m-value of material for leftup.    oblique mirror & -1 \\
mleft & 1 & m-value of material for left.      vertical mirror & -1 \\
mright & 1 & m-value of material for right.     vertical mirror & -1 \\
G & m/s2 & Gravitation norm. 0 value disables G effects. & 0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/Guide_honeycomb.comp}{Source code} for \texttt{Guide\_honeycomb.comp}.
\end{itemize}
\IfFileExists{Guide_honeycomb_static.tex}{\input{Guide_honeycomb_static.tex}}{}