\section{The \texttt{PerfectCrystal} McStas Component}
Based on a perfect crystal component by: Miguel A. Gonzalez, A. Dianoux June 2013 (ILL)

Changelog:
Version 1.1
- BUGFIX: correct neutron energy shift in Doppler mode
- added option 'debyescherrer' to select analyzer geometry
- added option 'facette' to approximate analyzer sphere by small, flat crystals

Version 1.0
- inital release

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Markus Appel
  \item \textbf{Origin:} ILL / FAU Erlangen-Nuernberg
  \item \textbf{Date:} 2015-12-21
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
Perfect crystal component, primarily for use as monochromator and analyzer in
backscattering spectrometers. Reflection from a single Bragg reflex of a flat or
spherical surface is simulated using a Darwin, Ewald or Gaussian profile. Doppler
movement of the monochromator is supported as well.

Orientation of the crystal surface is *different* from other monochromator components!
Gravitational energy shift for tall analyzers should work in principle, but it not tested yet.
See the parameter description on how to define the geometry and properties.

[1] Website for Backscattering Spectroscopy: http://www.ill.eu/sites/BS-review/index.htm

Examples:
IN16B (ILL) Si111 large angle analyzers (approximate dimensions):
PerfectCrystal(radius=2, lambda=6.2708, sigma=0.24e-3,
ttmin=40, ttmax=165, phimin=-45, phimax=+45, centerfocus=1)

IN16B (ILL) Si111 Doppler monochromator:
PerfectCrystal(radius=2.165, lambda=6.2708, sigma=0.24e-3,
width = 0.500, height = 0.250, centerfocus=0,
speed = 4.7, amplitude = 0.075, exclusive=1)
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
ttmin & deg &  & NAN \\
ttmax & deg & analyzer coverage angle in horizontal xz-plane between -180 and 180 & NAN \\
tt0 & deg &  & NAN \\
ttwidth & deg & horizontal coverage as center and full width & NAN \\
width & m & absolute width & NAN \\
phimin & deg &  & NAN \\
phimax & deg & vertical analyzer coverage between -90 and 90 (-180 and 180 if debyescherrer==1) & NAN \\
phi0 & deg &  & NAN \\
phiwidth & deg & vertical coverage as center and full width & NAN \\
height & m & absolute height (only if debyescherrer==0) & NAN \\
debyescherrer & -180...180 & (0/1)   bend analyzer following a Debye-Scherrer ring along scattering angle tt (twotheta) (phi = & 0 \\
facette & m & width of square crystal facettes arranged on the spherical surface (set 0 to disable). Default: 0 Warning: Facettation will fail at the poles along +-y axis. & 0 \\
facette\_xi & deg & random misalignemt of each facette. Default: 0 & 0 \\
centerfocus & 0/1 & Component origin is the center of the analyzer sphere if 1, if set to 0 the origin is on the analyzer surface. Default: 0 & 0 \\
radius & m & Radius of curvature, set to 0 for a flat surface. Default: 0 & 0 \\
tau & A\textasciicircum{}-1 & Scattering vector of the reflex (sometimes also called Q...) & NAN \\
lambda & A & Alternatively to tau: backscattered wavelength & NAN \\
R0 &  & Peak reflectivity. Default: 1 & 1.0 \\
dtauovertau & 1 & Plateau width of the Ewald/Darwin curve (see & NAN \\
dtauovertau\_ext &  & Relative variation of tau (randomized for each trajectory, full width) & 0 \\
ewald & 0/1 & Use Ewald curve if 1, Darwin curve if 0. Default: 1 (Ewald) & 1 \\
sigma & meV & Width of the Gaussian reflectivity curve in meV (corresponding to the energy resolution). (The width will be transformed and the Gaussian is actually calculated in k-space.) & NAN \\
ismirror & 0/1 & Simply reflect all neutrons if 1. Good for debugging/visualization. Default: 0 & 0 \\
speed & m/s & Maximum Doppler speed. The actual monochromator velocity is randomized between -speed and +speed. Default: 0 & 0 \\
amplitude & m & Amplitude of the Doppler movement. Default: 0 & 0 \\
smartphase & 0/1 & Optimize Doppler phase for better MC efficiency if set to 1. *WARNING:* Experimental option! Always compare to a simulation without smartphase. Better do not use smartwidth with Ewald/Darwin curves due to their endless tails. Default: 0 & 0 \\
smartwidth & meV & Half width of the possible energy reflection window for smartphase. Default: 5*sigma OR 10*2*dtauovertau*E0 & NAN \\
exclusive & 0/1 & If set to 1, absorb all neutrons that missed the monochromator/analyzer surface. Default: 0 & 0 \\
transmit & 0...1 & Monte-Carlo probability of transmitting an event through the monochromator/analyzer surface. (Events with R=1.0 for DarwinE/Ewald curves are always reflected!). Default: 0 & 0 \\
verbose &  &  & 0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/PerfectCrystal.comp}{Source code} for \texttt{PerfectCrystal.comp}.
\end{itemize}
\IfFileExists{PerfectCrystal_static.tex}{\input{PerfectCrystal_static.tex}}{}