\section{The \texttt{SANSNanodiscsFast} McStas Component}
A sample of monodisperse phospholipid bilayer nanodiscs in solution (water).

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Martin Cramer Pedersen (mcpe@nbi.dk)
  \item \textbf{Origin:} KU-Science
  \item \textbf{Date:} October 17, 2012
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
A component very similar to EmptyNanodiscs.comp - however, the scattering
profile is only computed once, and linear interpolation is the used to
simulate the instrument.
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
NumberOfQBins &  & Number of points generated in inital scattering profile. & 200 \\
AxisRatio &  & Axis ratio of the bilayer patch. & 1.4 \\
NumberOfLipids &  & Number of lipids per nanodisc. & 130.0 \\
AreaPerLipidHeadgroup & AA\textasciicircum{}2 & Area per lipid headgroup - default is POPC. & 65.0 \\
HeightOfMSP & AA & Height of the belt protein - default is MSP1D1. & 24.0 \\
VolumeOfOneMSP & AA\textasciicircum{}3 & Volume of one belt protein - default is MSP1D1. & 26296.5 \\
VolumeOfHeadgroup & AA\textasciicircum{}3 & Volume of one lipid headgroup - default is POPC. & 319.0 \\
VolumeOfCH2Tail & AA\textasciicircum{}3 & Volume of the CH2-chains of one lipid - default is POPC. & 818.8 \\
VolumeOfCH3Tail & AA\textasciicircum{}3 & Volume of the CH3-tails of one lipid - default is POPC. & 108.6 \\
ScatteringLengthOfOneMSP & cm & Scattering length of one belt protein - default is MSP1D1. & 8.8E-10 \\
ScatteringLengthOfHeadgroup & cm & Scattering length of one lipid headgroup - default is POPC. & 7.05E-12 \\
ScatteringLengthOfCH2Tail & cm & Scattering length of the CH2-chains of one lipid - default is POPC. & -1.76E-12 \\
ScatteringLengthOfCH3Tail & cm & Scattering length of the CH3-tails of one lipid - default is POPC. & -9.15E-13 \\
Roughness &  & Factor used to smear the interfaces of the nanodisc. & 5.0 \\
Concentration & mM & Concentration of sample. & 0.01 \\
RhoSolvent & cm/AA\textasciicircum{}3 & Scattering length density of solvent - default is D2O. & 6.4e-14 \\
AbsorptionCrosssection & 1/m & Absorption cross section of the sample. & 0.0 \\
\textbf{xwidth} & m & Dimension of component in the x-direction. &  \\
\textbf{yheight} & m & Dimension of component in the y-direction. &  \\
\textbf{zdepth} & m & Dimension of component in the z-direction. &  \\
\textbf{SampleToDetectorDistance} & m & Distance from sample to detector (for focusing the scattered neutrons). &  \\
\textbf{DetectorRadius} & m & Radius of the detector (for focusing the scattered neutrons). &  \\
qMin & AA\textasciicircum{}-1 & Lowest q-value, for which a point is generated in the scattering profile & 0.001 \\
qMax & AA\textasciicircum{}-1 & Highest q-value, for which a point is generated in the scattering profile & 1.0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/SANSNanodiscsFast.comp}{Source code} for \texttt{SANSNanodiscsFast.comp}.
\end{itemize}
\IfFileExists{SANSNanodiscsFast_static.tex}{\input{SANSNanodiscsFast_static.tex}}{}