\section{The \texttt{SANSEllipticCylinders} McStas Component}
A sample of monodisperse cylindrical particles with elliptic cross section in
solution.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Martin Cramer Pedersen (mcpe@nbi.dk)
  \item \textbf{Origin:} KU-Science
  \item \textbf{Date:} October 17, 2012
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
A component simulating the scattering from a box-shaped, thin solution
of monodisperse, cylindrical particles with elliptic cross section.
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
R1 & AA & First semiaxis of the cross section of the & 20.0 \\
R2 & AA & Second semiaxis of the cross section of the & 40.0 \\
Height & AA & Height of the elliptic cylinder. & 100.0 \\
Concentration & mM & Concentration of sample. & 0.01 \\
DeltaRho & cm/AA\textasciicircum{}3 & Excess scattering length density of the & 1.0e-14 \\
AbsorptionCrosssection & 1/m & Absorption cross section of the sample. & 0.0 \\
\textbf{xwidth} & m & Dimension of component in the x-direction. &  \\
\textbf{yheight} & m & Dimension of component in the y-direction. &  \\
\textbf{zdepth} & m & Dimension of component in the z-direction. &  \\
\textbf{SampleToDetectorDistance} & m & Distance from sample to detector (for &  \\
\textbf{DetectorRadius} & m & Radius of the detector (for focusing the &  \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/SANSEllipticCylinders.comp}{Source code} for \texttt{SANSEllipticCylinders.comp}.
\end{itemize}
\IfFileExists{SANSEllipticCylinders_static.tex}{\input{SANSEllipticCylinders_static.tex}}{}