\section{The \texttt{SANSPDBFast} McStas Component}
A sample describing a thin solution of proteins using linear interpolation
to increase computational speed. This components must be compiled with the
-lgsl and -lgslcblas flags (and possibly linked to the appropriate libraries).

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Martin Cramer Pedersen (mcpe@nbi.dk) and S\&oslash;ren Kynde (kynde@nbi.dk)
  \item \textbf{Origin:} KU-Science
  \item \textbf{Date:} October 17, 2012
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
This components expands the formfactor amplitude of the protein on spherical
harmonics and computes the scattering profile using these. The expansion is
done on amino-acid level and does not take hydration layer into account.
The component must have a valid .pdb-file as an argument.

This is fast implementation of the SANSPDB sample component.
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
RhoSolvent & AA & Scattering length density of the buffer - default is 100\% D2O. & 9.4e-14 \\
Concentration & mM & Concentration of sample. & 0.01 \\
AbsorptionCrosssection & 1/m & Absorption cross section of the sample. & 0.0 \\
\textbf{xwidth} & m & Dimension of component in the x-direction. &  \\
\textbf{yheight} & m & Dimension of component in the y-direction. &  \\
\textbf{zdepth} & m & Dimension of component in the z-direction. &  \\
\textbf{SampleToDetectorDistance} & m & Distance from sample to detector (for focusing the scattered neutrons). &  \\
\textbf{DetectorRadius} & m & Radius of the detector (for focusing the scattered neutrons). &  \\
qMin & AA\textasciicircum{}-1 & Lowest q-value, for which a point is generated in the scattering profile & 0.001 \\
qMax & AA\textasciicircum{}-1 & Highest q-value, for which a point is generated in the scattering profile & 0.5 \\
NumberOfQBins &  & Number of points generated in inital scattering profile. & 200 \\
PDBFilepath &  & Path to the file describing the high resolution structure of the protein. & "PDBfile.pdb" \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/SANSPDBFast.comp}{Source code} for \texttt{SANSPDBFast.comp}.
\end{itemize}
\IfFileExists{SANSPDBFast_static.tex}{\input{SANSPDBFast_static.tex}}{}