\section{The \texttt{SANSCurve} McStas Component}
A component mimicking the scattering from a given I(q)-curve by using
linear interpolation between the given points.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Søren Kynde (kynde@nbi.dk)
  \item \textbf{Origin:} KU-Science
  \item \textbf{Date:} October 17, 2012
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
A box-shaped component simulating the scattering from any given I(q)-curve.
The component uses linear interpolation to generate the points necessary to
compute the scattering of any given neutron.
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
DeltaRho & cm/AA\textasciicircum{}3 & Excess scattering length density of the particles. & 1.0e-14 \\
Volume & AA\textasciicircum{}3 & Volume of the particles. & 1000.0 \\
Concentration & mM & Concentration of sample. & 0.01 \\
AbsorptionCrosssection & 1/m & Absorption cross section of the sample. & 0.0 \\
\textbf{xwidth} & m & Dimension of component in the x-direction. &  \\
\textbf{yheight} & m & Dimension of component in the y-direction. &  \\
\textbf{zdepth} & m & Dimension of component in the z-direction. &  \\
\textbf{SampleToDetectorDistance} & m & Distance from sample to detector (for focusing the scattered neutrons). &  \\
\textbf{DetectorRadius} & m & Radius of the detector (for focusing the scattered neutrons). &  \\
FileWithCurve &  & Datafile with the given I(q). & "Curve.dat" \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/SANSCurve.comp}{Source code} for \texttt{SANSCurve.comp}.
\end{itemize}
\IfFileExists{SANSCurve_static.tex}{\input{SANSCurve_static.tex}}{}