\section{The \texttt{SANSLiposomes} McStas Component}
A sample of polydisperse liposomes in solution (water).

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Martin Cramer Pedersen (mcpe@nbi.dk)
  \item \textbf{Origin:} KU-Science
  \item \textbf{Date:} October 17, 2012
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
A component simulating the scattering from a box-shaped, thin solution (water)
of liposomes described by a pentuple-shell model.
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
Radius & AA & Average thickness of the liposomes. & 800.0 \\
Thickness & AA & Thickness of the bilayer. & 38.89 \\
SigmaRadius &  & Relative Gaussian deviation of the radius in the distribution of liposomes. & 0.20 \\
VolumeOfHeadgroup & AA\textasciicircum{}3 & Volume of one lipid headgroup - default is POPC. & 319.0 \\
VolumeOfCH2Tail & AA\textasciicircum{}3 & Volume of the CH2-chains of one lipid - default is POPC. & 818.8 \\
VolumeOfCH3Tail & AA\textasciicircum{}3 & Volume of the CH3-tails of one lipid - default is POPC. & 108.6 \\
ScatteringLengthOfHeadgroup & cm & Scattering length of one lipid headgroup - default is POPC in D2O. & 7.05E-12 \\
ScatteringLengthOfCH2Tail & cm & Scattering length of the CH2-chains of one lipid - default is POPC in D2O. & -1.76E-12 \\
ScatteringLengthOfCH3Tail & cm & Scattering length of the CH3-tails of one lipid - default is POPC in D2O. & -9.15E-13 \\
Concentration & mM & Concentration of sample. & 0.01 \\
RhoSolvent & cm/AA\textasciicircum{}3 & Scattering length density of solvent - default is D2O. & 6.4e-14 \\
AbsorptionCrosssection & 1/m & Absorption cross section of the sample. & 0.0 \\
\textbf{xwidth} & m & Dimension of component in the x-direction. &  \\
\textbf{yheight} & m & Dimension of component in the y-direction. &  \\
\textbf{zdepth} & m & Dimension of component in the z-direction. &  \\
\textbf{SampleToDetectorDistance} & m & Distance from sample to detector (for focusing the scattered neutrons). &  \\
\textbf{DetectorRadius} & m & Radius of the detector (for focusing the scattered neutrons). &  \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/SANSLiposomes.comp}{Source code} for \texttt{SANSLiposomes.comp}.
\end{itemize}
\IfFileExists{SANSLiposomes_static.tex}{\input{SANSLiposomes_static.tex}}{}