\section{The \texttt{Transmission\_polarisatorABSnT} McStas Component}
Transmission V-polarisator including absorption by Fe in the supermirror.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Andreas Ostermann
  \item \textbf{Origin:} TUM
  \item \textbf{Date:} 2004
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
Transmission V-polarisator including absorption by Fe in the supermirror.

Example: Gravity_guide(w1=0.1, h1=0.1, w2=0.1, h2=0.1, l=12,
R0=0.99, Qc=0.021, alpha=6.07, m=1.0, W=0.003, k=1, d=0.0005)
Example: Transmission_polarisatorABSnT(w1=0.050, h1=0.050,
w2=0.050, h2=0.050, l=2.700,
waferD=0.0003, FeD=2.16e-06,
Si_i=0.2, Si_a=0.215,
R0=0.99, Qc=0.02174, alpha=4.25, W=0.001,
mleft=1.2, mright=1.2, mtop=1.2, mbottom=1.2,
R0_up=0.99, Qc_up=0.014, alpha_up=2.25, W_up=0.0025, mup=1.0,
R0_down=0.99, Qc_down=0.02174, alpha_down=3.8, W_down=0.00235, mdown=2.5)
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
\textbf{w1} & m & Width at the polarizer entry &  \\
\textbf{h1} & m & Height at the polarizer entry &  \\
\textbf{w2} & m & Width at the polarizer exit &  \\
\textbf{h2} & m & Height at the polarizer exit &  \\
\textbf{l} & m & length of polarizer &  \\
\textbf{waferD} & m & Thickness of Si wafer &  \\
\textbf{Si\_i} & barns & Scattering cross section per atom (barns) &  \\
\textbf{Si\_a} & barns & Absorption cross section per atom (barns) at 2200m/s &  \\
\textbf{FeD} & m & Thickness of Fe wafer &  \\
R0 & 1 & Low-angle reflectivity of the outer guide & 0.99 \\
Qc & AA-1 & Critical scattering vector of the outer guide & 0.02174 \\
alpha & AA & Slope of reflectivity of the outer guide & 4.25 \\
W & AA-1 & Width of supermirror cut-off of the outer guide & 0.001 \\
R0\_up & 1 & Low-angle reflectivity of the Fe/Si-wafer for spin up neutrons & 0.99 \\
Qc\_up & AA-1 & Critical scattering vector of the Fe/Si-wafer for spin up neutrons & 0.0109 \\
alpha\_up & AA & Slope of reflectivity of the Fe/Si-wafer for spin up neutrons & 4.25 \\
W\_up & AA-1 & Width of supermirror cut-off of the Fe/Si-wafer for spin up neutrons & 0.0025 \\
R0\_down & 1 & Low-angle reflectivity of the Fe/Si-wafer for spin down neutrons & 0.99 \\
Qc\_down & AA-1 & Critical scattering vector of the Fe/Si-wafer for spin down neutrons & 0.02174 \\
alpha\_down & AA & Slope of reflectivity of the Fe/Si-wafer for spin down neutrons & 6.25 \\
W\_down & AA-1 & Width of supermirror cut-off of the Fe/Si-wafer for spin down neutrons & 0.001 \\
mleft & 1 & m-value of material for left.   vert. mirror of the outer guide & -1 \\
mright & 1 & m-value of material for right.  vert. mirror of the outer guide & -1 \\
mtop & 1 & m-value of material for top.    horz. mirror of the outer guide & -1 \\
mbottom & 1 & m-value of material for bottom. horz. mirror of the outer guide & -1 \\
mup & 1 & m-value of the Fe/Si-wafer for spin up neutrons & -1 \\
mdown & 1 & m-value of the Fe/Si-wafer for spin down neutrons & -1 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/Transmission_polarisatorABSnT.comp}{Source code} for \texttt{Transmission\_polarisatorABSnT.comp}.
\end{itemize}
\IfFileExists{Transmission_polarisatorABSnT_static.tex}{\input{Transmission_polarisatorABSnT_static.tex}}{}