\section{The \texttt{Transmission\_V\_polarisator} McStas Component}
Transmission V-polarisator including absorption by Fe in the supermirror. Experimentally benchmarked.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Andreas Ostermann (additions from Michael Schneider, SNAG)
  \item \textbf{Origin:} TUM
  \item \textbf{Date:} 2024
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
Transmission V-polarisator including absorption by Fe in the supermirror.

Example: Transmission_V_polarisator(w1=0.050, h1=0.050,
w2=0.050, h2=0.050, l=2.700,
waferD=0.0003, FeD=2.16e-06,
Si_i=0.2, Si_a=0.215,
R0=0.99, Qc=0.02174, alpha=4.25, W=0.001,
mleft=1.2, mright=1.2, mtop=1.2, mbottom=1.2,
reflectUP="measured_up_q.dat",reflectDW="measured_dw_q.dat")
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
reflectUP & str & Reflectivity profile of the FeSi-wafer for spin-up neutrons; columns [q,R] & 0 \\
reflectDW & str & Reflectivity profile of the FeSi-wafer for spin-down neutrons; columns [q,R] & 0 \\
\textbf{w1} & m & Width at the polarizer entry &  \\
\textbf{h1} & m & Height at the polarizer entry &  \\
\textbf{w2} & m & Width at the polarizer exit &  \\
\textbf{h2} & m & Height at the polarizer exit &  \\
\textbf{l} & m & length of polarizer &  \\
\textbf{waferD} & m & Thickness of Si wafer &  \\
\textbf{Si\_i} & barns & Scattering cross section per atom (barns) &  \\
\textbf{Si\_a} & barns & Absorption cross section per atom (barns) at 2200m/s &  \\
\textbf{FeD} & m & Thickness of Fe in supermirror, Ti is neglected &  \\
R0 & 1 & Low-angle reflectivity of the outer guide & 0.99 \\
Qc & AA-1 & Critical scattering vector of the outer guide & 0.02174 \\
alpha & AA & Slope of reflectivity of the outer guide & 4.25 \\
W & AA-1 & Width of supermirror cut-off of the outer guide & 0.001 \\
mleft & 1 & m-value of material for left.   vert. mirror of the outer guide & -1 \\
mright & 1 & m-value of material for right.  vert. mirror of the outer guide & -1 \\
mtop & 1 & m-value of material for top.    horz. mirror of the outer guide & -1 \\
mbottom & 1 & m-value of material for bottom. horz. mirror of the outer guide & -1 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/contrib/Transmission_V_polarisator.comp}{Source code} for \texttt{Transmission\_V\_polarisator.comp}.
  \item P. B\&ouml;ni, W. M\&uuml;nzer and A. Ostermann: \textless{}a href="https://doi.org/10.1016/j.physb.2009.06.031"\textgreater{}Physica B: Condensed Matter Volume 404, Issue 17, 1 September 2009, Pages 2620-2623\textless{}/a\textgreater{}
\end{itemize}
\IfFileExists{Transmission_V_polarisator_static.tex}{\input{Transmission_V_polarisator_static.tex}}{}