\section{The \texttt{Powder\_process} McStas Component}
Port of the PowderN process to the Union components

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Mads Bertelsen
  \item \textbf{Origin:} University of Copenhagen
  \item \textbf{Date:} 20.08.15
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
This Union_process is based on the PowderN.comp component originally written
by P. Willendrup, L. Chapon, K. Lefmann, A.B.Abrahamsen, N.B.Christensen,
E.M.Lauridsen.

Part of the Union components, a set of components that work together and thus
sperates geometry and physics within McStas.
The use of this component requires other components to be used.

1) One specifies a number of processes using process components like this one
2) These are gathered into material definitions using Union_make_material
3) Geometries are placed using Union_box / Union_cylinder, assigned a material
4) A Union_master component placed after all of the above

Only in step 4 will any simulation happen, and per default all geometries
defined before the master, but after the previous will be simulated here.

There is a dedicated manual available for the Union_components
Algorithm:
Described elsewhere
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
reflections & string & Input file for reflections. No scattering if NULL or "" [string] & "NULL" \\
packing\_factor & 1 & How dense is the material compared to optimal 0-1 & 1 \\
Vc & AA\textasciicircum{}3 & Volume of unit cell=nb atoms per cell/density of atoms. & 0 \\
delta\_d\_d & 0/1 & Global relative delta\_d\_d/d broadening when the 'w' column is not available. Use 0 if ideal. & 0 \\
DW & 1 & Global Debye-Waller factor when the 'DW' column is not available. Use 1 if included in F2 & 0 \\
nb\_atoms & 1 & Number of sub-unit per unit cell, that is ratio of sigma for chemical formula to sigma per unit cell & 1 \\
d\_phi & deg & Angle corresponding to the vertical angular range to focus to, e.g. detector height. 0 for no focusing. & 0 \\
density & g/cm\textasciicircum{}3 & Density of material. rho=density/weight/1e24*N\_A. & 0 \\
weight & g/mol & Atomic/molecular weight of material. & 0 \\
barns & 1 & Flag to indicate if |F|\textasciicircum{}2 from 'reflections' is in barns or fm\textasciicircum{}2 (barns=1 for laz, barns=0 for lau type files). & 1 \\
Strain & ppm & Global relative delta\_d\_d/d shift when the 'Strain' column is not available. Use 0 if ideal. & 0 \\
interact\_fraction & 1 & How large a part of the scattering events should use this process 0-1 (sum of all processes in material = 1) & -1 \\
format & no quotes & Name of the format, or list of column indexes (see Description). & \{0, 0, 0, 0, 0, 0, 0, 0, 0\} \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/union/Powder_process.comp}{Source code} for \texttt{Powder\_process.comp}.
\end{itemize}
\IfFileExists{Powder_process_static.tex}{\input{Powder_process_static.tex}}{}