\section{The \texttt{MCPL\_input\_once} McStas Component}
Source-like component that reads neutron state parameters from a MCPL-file one time.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Gregory S Tucker
  \item \textbf{Origin:} European Spallation Source ERIC
  \item \textbf{Date:} Sep 2024
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
Source-like component that reads neutron state parameters from a MCPL-file one time.

MCPL is short for Monte Carlo Particle List, and is a format for sharing events
between e.g. MCNP(X), Geant4 and McStas.

When used with MPI, the file contents are shared between workers with each accessing
approximately (#events in the file) / (#MPI nodes)

%BUGS
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
filename & str & Name of neutron mcpl file to read. & 0 \\
polarisationuse &   & If !=0 read polarisation vectors from file. & 1 \\
Emin & meV & Lower energy bound. Particles found in the MCPL-file below the limit are skipped. & 0 \\
Emax & meV & Upper energy bound. Particles found in the MCPL-file above the limit are skipped. & FLT\_MAX \\
v\_smear & 1 & Relative fraction for randomness in replayed particle velocity v *= (1 + v\_smear * randpm1()) & 0 \\
pos\_smear & m & Maximum extent of random position for replayed particles & 0 \\
dir\_smear & deg & Maximum deviation of random direction for replayed particles & 0 \\
always\_smear &   & Finite values force particle property smearing for all particles & 0 \\
preload &   & Load particles during INITIALIZE. On GPU preload is forced. & 0 \\
verbose &   & Finite values may cause extra output (at some point in the future) & 0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/misc/MCPL_input_once.comp}{Source code} for \texttt{MCPL\_input\_once.comp}.
\end{itemize}
\IfFileExists{MCPL_input_once_static.tex}{\input{MCPL_input_once_static.tex}}{}