\section{The \texttt{V\_sample} McStas Component}
Vanadium sample.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Kim Lefmann and Kristian Nielsen
  \item \textbf{Origin:} Risoe
  \item \textbf{Date:} 15.4.98
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
A Double-cylinder shaped incoherent scatterer (a V-sample)
with both elastic and quasielastic (Lorentzian) components.
No multiple scattering. Absorbtion included.
The shape of the sample may be a box with dimensions xwidth, yheight, zthick.
The area to scatter to is a disk of radius 'focus_r' situated at the target.
This target area may also be rectangular if specified focus_xw and focus_yh
or focus_aw and focus_ah, respectively in meters and degrees.
The target itself is either situated according to given coordinates (x,y,z),
or defined with the relative target_index of the component to focus
to (next is +1).
This target position will be set to its AT position. When targeting to
centered components, such as spheres or cylinders, define an Arm component
where to focus to.

Example: V_sample(radius_i=0.001,radius_o=0.01,h=0.02,focus_r=0.035,pack=1,
target_index=1)
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
radius & m & Outer radius of sample in (x,z) plane & 0 \\
thickness & m & Thickness of outer wall & 0 \\
zdepth & m & depth of box sample & 0 \\
Vc &  & Unit cell volume [AA\textasciicircum{}3] & 13.827 \\
sigma\_abs & barns & Absorbtion cross section pr. unit cell & 5.08 \\
sigma\_inc & barns & Incoherent scattering cross section pr. unit cell & 5.08 \\
radius\_i & m & radius-thickness & 0 \\
radius\_o & m & Same as radius & 0 \\
h & m & Same as yheight & 0 \\
focus\_r & m & Radius of disk containing target. Use 0 for full space & 0 \\
pack & 1 & Packing factor & 1 \\
frac & 1 & MC Probability for scattering the ray; otherwise penetrate & 1 \\
f\_QE & 1 & Fraction of quasielastic scattering (rest is elastic) & 0 \\
gamma & 1 & Lorentzian width of quasielastic broadening (HWHM) & 0 \\
target\_x &  &  & 0 \\
target\_y & m & position of target to focus at & 0 \\
target\_z &  &  & 0 \\
focus\_xw & m & horiz. dimension of a rectangular area & 0 \\
focus\_yh & m & vert.  dimension of a rectangular area & 0 \\
focus\_aw & deg & angular width dimension of a rectangular area & 0 \\
focus\_ah & deg & angular height dimension of a rectangular area & 0 \\
xwidth & m & horiz. dimension of sample & 0 \\
yheight & m & vert.  dimension of sample & 0 \\
zthick & m & Same as zdepth & 0 \\
rad\_sphere & m & Radius for a spherical sample & 0 \\
sig\_a & barns & Same as sigma\_abs & 0 \\
sig\_i & barns & Same as sigma\_inc & 0 \\
V0 &  & Same as Vc [AA\textasciicircum{}3] & 0 \\
target\_index & 1 & relative index of component to focus at, e.g. next is +1 & 0 \\
multiples & 1 & Apply crude estimate for multiple scattering & 1 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/obsolete/V_sample.comp}{Source code} for \texttt{V\_sample.comp}.
  \item \textless{}A HREF="http://neutron.risoe.dk/mcstas/components/tests/v\_sample/"\textgreater{}Test
  \item results\textless{}/A\textgreater{} (not up-to-date).
  \item The test/example instrument \textless{}a href="../examples/vanadium\_example.instr"\textgreater{}vanadium\_example.instr\textless{}/a\textgreater{}.
  \item The test/example instrument \textless{}a href="../examples/QENS\_test.instr"\textgreater{}QENS\_test.instr\textless{}/a\textgreater{}.
\end{itemize}
\IfFileExists{V_sample_static.tex}{\input{V_sample_static.tex}}{}