\section{The \texttt{SasView\_core\_shell\_bicelle\_aniso} McStas Component}
SasView core\_shell\_bicelle model component as sample description.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Jose Robledo
  \item \textbf{Origin:} FZJ / DTU / ESS DMSC
  \item \textbf{Date:} 
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
SasView_core_shell_bicelle component, generated from core_shell_bicelle.c in sasmodels.

Example:
SasView_core_shell_bicelle_aniso(radius, thick_rim, thick_face, length, sld_core, sld_face, sld_rim, sld_solvent, theta, phi,
model_scale=1.0, model_abs=0.0, xwidth=0.01, yheight=0.01, zdepth=0.005, R=0,
int target_index=1, target_x=0, target_y=0, target_z=1,
focus_xw=0.5, focus_yh=0.5, focus_aw=0, focus_ah=0, focus_r=0,
pd_radius=0.0, pd_thick_rim=0.0, pd_thick_face=0.0, pd_length=0.0, pd_theta=0.0, pd_phi=0.0)
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
radius & Ang & ([0, inf]) Cylinder core radius. & 80 \\
thick\_rim & Ang & ([0, inf]) Rim shell thickness. & 10 \\
thick\_face & Ang & ([0, inf]) Cylinder face thickness. & 10 \\
length & Ang & ([0, inf]) Cylinder length. & 50 \\
sld\_core & 1e-6/Ang\textasciicircum{}2 & ([-inf, inf]) Cylinder core scattering length density. & 1 \\
sld\_face & 1e-6/Ang\textasciicircum{}2 & ([-inf, inf]) Cylinder face scattering length density. & 4 \\
sld\_rim & 1e-6/Ang\textasciicircum{}2 & ([-inf, inf]) Cylinder rim scattering length density. & 4 \\
sld\_solvent & 1e-6/Ang\textasciicircum{}2 & ([-inf, inf]) Solvent scattering length density. & 1 \\
theta &  &  & 90 \\
phi &  &  & 0 \\
model\_scale &   & Global scale factor for scattering kernel. For systems without inter-particle interference, the form factors can be related to the scattering intensity by the particle volume fraction. & 1.0 \\
model\_abs &   & Absorption cross section density at 2200 m/s. & 0.0 \\
xwidth & m & ([-inf, inf]) Horiz. dimension of sample, as a width. & 0.01 \\
yheight & m & ([-inf, inf]) vert . dimension of sample, as a height for cylinder/box & 0.01 \\
zdepth & m & ([-inf, inf]) depth of sample & 0.005 \\
R & m & Outer radius of sample in (x,z) plane for cylinder/sphere. & 0 \\
target\_x & m & relative focus target position. & 0 \\
target\_y & m & relative focus target position. & 0 \\
target\_z & m & relative focus target position. & 1 \\
target\_index &   & Relative index of component to focus at, e.g. next is +1. & 1 \\
focus\_xw & m & horiz. dimension of a rectangular area. & 0.5 \\
focus\_yh & m & , vert. dimension of a rectangular area. & 0.5 \\
focus\_aw & deg & , horiz. angular dimension of a rectangular area. & 0 \\
focus\_ah & deg & , vert. angular dimension of a rectangular area. & 0 \\
focus\_r & m & case of circular focusing, focusing radius. & 0 \\
pd\_radius &  & (0,inf) defined as (dx/x), where x is de mean value and dx the standard devition of the variable. & 0.0 \\
pd\_thick\_rim &  & (0,inf) defined as (dx/x), where x is de mean value and dx the standard devition of the variable. & 0.0 \\
pd\_thick\_face &  & (0,inf) defined as (dx/x), where x is de mean value and dx the standard devition of the variable. & 0.0 \\
pd\_length &  & (0,inf) defined as (dx/x), where x is de mean value and dx the standard devition of the variable. & 0.0 \\
pd\_theta &  & (0,360) defined as (dx/x), where x is de mean value and dx the standard devition of the variable. & 0.0 \\
pd\_phi &  & (0,360) defined as (dx/x), where x is de mean value and dx the standard devition of the variable & 0.0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/sasmodels/SasView_core_shell_bicelle_aniso.comp}{Source code} for \texttt{SasView\_core\_shell\_bicelle\_aniso.comp}.
\end{itemize}
\IfFileExists{SasView_core_shell_bicelle_aniso_static.tex}{\input{SasView_core_shell_bicelle_aniso_static.tex}}{}