\section{The \texttt{SasView\_pearl\_necklace} McStas Component}
SasView pearl\_necklace model component as sample description.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Jose Robledo
  \item \textbf{Origin:} FZJ / DTU / ESS DMSC
  \item \textbf{Date:} 
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
SasView_pearl_necklace component, generated from pearl_necklace.c in sasmodels.

Example:
SasView_pearl_necklace(radius, edge_sep, thick_string, num_pearls, sld, sld_string, sld_solvent,
model_scale=1.0, model_abs=0.0, xwidth=0.01, yheight=0.01, zdepth=0.005, R=0,
int target_index=1, target_x=0, target_y=0, target_z=1,
focus_xw=0.5, focus_yh=0.5, focus_aw=0, focus_ah=0, focus_r=0,
pd_radius=0.0, pd_thick_string=0.0)
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
radius & Ang & ([0, inf]) Mean radius of the chained spheres. & 80.0 \\
edge\_sep & Ang & ([0, inf]) Mean separation of chained particles. & 350.0 \\
thick\_string & Ang & ([0, inf]) Thickness of the chain linkage. & 2.5 \\
num\_pearls & none & ([1, inf]) Number of pearls in the necklace (must be integer). & 3 \\
sld & 1e-6/Ang\textasciicircum{}2 & ([-inf, inf]) Scattering length density of the chained spheres. & 1.0 \\
sld\_string & 1e-6/Ang\textasciicircum{}2 & ([-inf, inf]) Scattering length density of the chain linkage. & 1.0 \\
sld\_solvent & 1e-6/Ang\textasciicircum{}2 & ([-inf, inf]) Scattering length density of the solvent. & 6.3 \\
model\_scale &   & Global scale factor for scattering kernel. For systems without inter-particle interference, the form factors can be related to the scattering intensity by the particle volume fraction. & 1.0 \\
model\_abs &   & Absorption cross section density at 2200 m/s. & 0.0 \\
xwidth & m & ([-inf, inf]) Horiz. dimension of sample, as a width. & 0.01 \\
yheight & m & ([-inf, inf]) vert . dimension of sample, as a height for cylinder/box & 0.01 \\
zdepth & m & ([-inf, inf]) depth of sample & 0.005 \\
R & m & Outer radius of sample in (x,z) plane for cylinder/sphere. & 0 \\
target\_x & m & relative focus target position. & 0 \\
target\_y & m & relative focus target position. & 0 \\
target\_z & m & relative focus target position. & 1 \\
target\_index &   & Relative index of component to focus at, e.g. next is +1. & 1 \\
focus\_xw & m & horiz. dimension of a rectangular area. & 0.5 \\
focus\_yh & m & , vert. dimension of a rectangular area. & 0.5 \\
focus\_aw & deg & , horiz. angular dimension of a rectangular area. & 0 \\
focus\_ah & deg & , vert. angular dimension of a rectangular area. & 0 \\
focus\_r & m & case of circular focusing, focusing radius. & 0 \\
pd\_radius &  & (0,inf) defined as (dx/x), where x is de mean value and dx the standard devition of the variable. & 0.0 \\
pd\_thick\_string &  & (0,inf) defined as (dx/x), where x is de mean value and dx the standard devition of the variable & 0.0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/sasmodels/SasView_pearl_necklace.comp}{Source code} for \texttt{SasView\_pearl\_necklace.comp}.
\end{itemize}
\IfFileExists{SasView_pearl_necklace_static.tex}{\input{SasView_pearl_necklace_static.tex}}{}