\section{The \texttt{FZP\_simple} McStas Component}
Fresnel zone-plate as a thin object approximation.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} A Komar Ravn, and Erik B Knudsen
  \item \textbf{Origin:} NBI/DTU
  \item \textbf{Date:} Aug, 2015
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
A simple phenomenological thin-object approximation of a Fresnel Zone Plate.
This component was adapted for neutrons from the original component
written for helium scattering.
The focal length of the Zone Plate is determined by the formula:
\[f = 2*r*dr/(lambda)\]
If a diffraction order other than 1 is wanted the focal distance is scaled accordingly.
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
\textbf{rad} & m & Radius of  the zone-plate. &  \\
\textbf{dr} & m & Width of the outermost ring-slit. &  \\
bs0rad & m & Radius of the central blocking zone. & 0 \\
order & m & Use this diffaction order. & 1 \\
eta &   & Efficiency of the FZP. For neutrons and (order==1) typically \{5...30\}\%. Overrides the sigma\_x cross sections. & 0.1 \\
sigma\_abs & barn & 2200 m/s absorption cross section. & 0 \\
sigma\_inc & barn & Incoherent scattering cross section. & 0 \\
sigma\_coh & barn & Coherent scattering cross section. & 0 \\
rho & g/cm3 & Density of Zone plate material - used merely for absorption estimation. & 1 \\
thickness & m & Thickness of the FZP. Note that the FZP still is modelled as a thin object. The thickness is used in conjunction with the sigma\_x cross sections. & 0 \\
gamma &   & Duty cycle of the Zone plate - used merely for absorption estimation. & 0.5 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/optics/FZP_simple.comp}{Source code} for \texttt{FZP\_simple.comp}.
\end{itemize}
\IfFileExists{FZP_simple_static.tex}{\input{FZP_simple_static.tex}}{}