\section{The \texttt{Guide\_channeled} McStas Component}
Neutron guide with channels (bender section).

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Christian Nielsen
  \item \textbf{Origin:} Risoe
  \item \textbf{Date:} 1999
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
Models a rectangular guide tube centered on the Z axis. The entrance lies
in the X-Y plane.
The guide may be tapered, and may have vertical subdivisions (used for
bender devices).

There is a special rotating mode in order to approximate a Fermi Chopper
behaviour, in the case the neutron trajectory is nearly linear inside the
chopper slits, i.e. the neutrons are fast w/r/ to the chopper speed.
Slits are straight, but may be super-mirror coated. In this case, the
component is NOT centered, but located at its entry window. It should then
be shifted by -l/2.

Example: Guide_channeled(w1=0.1, h1=0.1, w2=0.1, h2=0.1, l=2.0,
R0=0.99, Qcx=0.0219, Qcy=0.0219, alphax=6.07, alphay=6.07, W=0.003, nslit=1,
d=0.0005, mx=1, my=1)

%BUGS
This component does not work with gravitation on. Use Guide_gravity.
This component does not work in multichannel focusing geometry.
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
\textbf{w1} & m & Width at the guide entry &  \\
\textbf{h1} & m & Height at the guide entry &  \\
w2 & m & Width at the guide exit & 0 \\
h2 & m & Height at the guide exit & 0 \\
\textbf{l} & m & Length of guide &  \\
R0 & 1 & Low-angle reflectivity & 0.995 \\
Qc & AA-1 & Critical scattering vector & 0 \\
alpha & AA & Slope of reflectivity & 0 \\
m & 1 & m-value of material. Zero means completely absorbing. & 0 \\
nslit & 1 & Number of channels in the guide (\textgreater{}= 1) & 1 \\
d & m & Thickness of subdividing absorbing walls & 0.0005 \\
Qcx & AA-1 & Critical scattering vector for left and right vertical mirrors in each channel & 0.0218 \\
Qcy & AA-1 & Critical scattering vector for top and bottom mirrors & 0.0218 \\
alphax & AA & Slope of reflectivity for left and right vertical mirrors in each channel & 4.38 \\
alphay & AA & Slope of reflectivity for top and bottom mirrors & 4.38 \\
W & AA-1 & Width of supermirror cut-off for all mirrors & 0.003 \\
mx & 1 & m-value of material for left and right vertical mirrors in each channel. Zero means completely absorbing. & 1 \\
my & 1 & m-value of material for top and bottom mirrors. Zero means completely absorbing. & 1 \\
nu & Hz & Rotation frequency (round/s) for Fermi Chopper approximation & 0 \\
phase & deg & Phase shift for the Fermi Chopper approximation & 0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/optics/Guide_channeled.comp}{Source code} for \texttt{Guide\_channeled.comp}.
\end{itemize}
\IfFileExists{Guide_channeled_static.tex}{\input{Guide_channeled_static.tex}}{}