\section{The \texttt{DivLambda\_monitor} McStas Component}
Divergence/wavelength monitor.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Kristian Nielsen
  \item \textbf{Origin:} Risoe
  \item \textbf{Date:} 1999
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
2D detector for intensity as a function of both horizontal divergence
and wavelength.

Example: DivLambda_monitor(nL=20, nh=20, filename="Output.div",
xmin=-0.1, xmax=0.1, ymin=-0.1, ymax=0.1,
maxdiv_h=2, Lmin=2, Lmax=10)
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
nL & 1 & Number of bins in wavelength & 20 \\
nh & 1 & Number of bins in divergence & 20 \\
nowritefile & 1 & If set, monitor will skip writing to disk & 0 \\
filename & string & Name of file in which to store the detector image & 0 \\
xmin & m & Lower x bound of detector opening & -0.05 \\
xmax & m & Upper x bound of detector opening & 0.05 \\
ymin & m & Lower y bound of detector opening & -0.05 \\
ymax & m & Upper y bound of detector opening & 0.05 \\
xwidth & m & Width of detector. Overrides xmin,xmax. & 0 \\
yheight & m & Height of detector. Overrides ymin,ymax. & 0 \\
maxdiv\_h & degrees & Maximal horizontal divergence detected & 2 \\
\textbf{Lmin} & AA & Minimum wavelength detected &  \\
\textbf{Lmax} & AA & Maximum wavelength detected &  \\
restore\_neutron & 1 & If set, the monitor does not influence the neutron state & 0 \\
nx & 1 &  & 0 \\
ny & 1 & Vector definition of "forward" direction wrt. divergence, to be used e.g. when the monitor is rotated into the horizontal plane. & 0 \\
nz & 1 &  & 1 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/monitors/DivLambda_monitor.comp}{Source code} for \texttt{DivLambda\_monitor.comp}.
\end{itemize}
\IfFileExists{DivLambda_monitor_static.tex}{\input{DivLambda_monitor_static.tex}}{}