\section{The \texttt{Flex\_monitor\_3D} McStas Component}
Flexible monitor.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Erik B Knudsen \& Peter Willendrup
  \item \textbf{Origin:} DTU Physics
  \item \textbf{Date:} Oct '20
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
A square 3D single monitor that measures intensity (or something else) as a function of two selectable variables or parameters.

Example: Flex_monitor_3D(nU1=20, nU2=20, nU3=20, filename="Output", ustring1="x", ustring2="y", ustring1="z", Umin1=-.1, Umax1=.1, Umin2=-.1, Umax2=.1, Umin3=-.1, Umax3=.1)
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
nU1 & 1 & Number of U1 channels & 20 \\
nU2 & 1 & Number of U1 channels & 20 \\
nU3 & 1 & Number of U3 channels & 20 \\
filename & string & Name of file in which to store the detector image & 0 \\
\textbf{Umin1} &  & Minimum U1 to detect &  \\
\textbf{Umax1} &  & Maximum U1 to detect &  \\
uid1 & 1 & Integer index of uservar to be monitored. Overrides ustring1. & -1 \\
ustring1 & string & Name of variable U1 (user or neutron state parameter as a string) to be monitored. & "" \\
\textbf{Umin2} &  & Minimum U1 to detect &  \\
\textbf{Umax2} &  & Maximum U1 to detect &  \\
uid2 & 1 & Integer index of uservar to be monitored. Overrides ustring2. & -1 \\
ustring2 & string & Name of variable U2 (user or neutron state parameter as a string) to be monitored. & "" \\
\textbf{Umin3} &  & Minimum U3 to detect &  \\
\textbf{Umax3} &  & Maximum U3 to detect &  \\
uid3 & 1 & Integer index of uservar to be monitored. Overrides ustring3. & -1 \\
ustring3 & string & Name of variable U3 (user or neutron state parameter as a string) to be monitored. & "" \\
restore\_neutron & 1 & If set, the monitor does not influence the neutron state & 0 \\
signal & string & Name of variable to be used as an additive signal to be monitored. Default is intensity. & "p" \\
nowritefile & 1 & Flag to indicate if monitor should not save any data. & 0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/monitors/Flex_monitor_3D.comp}{Source code} for \texttt{Flex\_monitor\_3D.comp}.
\end{itemize}
\IfFileExists{Flex_monitor_3D_static.tex}{\input{Flex_monitor_3D_static.tex}}{}