\section{The \texttt{Res\_sample} McStas Component}
Sample for resolution function calculation.

\subsection*{Identification}
\begin{itemize}
  \item \textbf{Site:} 
  \item \textbf{Author:} Kristian Nielsen
  \item \textbf{Origin:} Risoe
  \item \textbf{Date:} 1999
\end{itemize}

\subsection*{Description}
\begin{lstlisting}
An inelastic sample with completely uniform scattering in both Q and
energy. This sample is used together with the Res_monitor component and
(optionally) the mcresplot front-end to compute the resolution function of
triple-axis or inverse-geometry time-of-flight instruments.

The shape of the sample is either a hollow cylinder or a rectangular box. The
hollow cylinder shape is specified with an inner and outer radius.
The box is specified with dimensions xwidth, yheight, zdepth.

The scattered neutrons will have directions towards a given disk and
energies betweed E0-dE and E0+dE.
This target area may also be rectangular if specified focus_xw and focus_yh
or focus_aw and focus_ah, respectively in meters and degrees.
The target itself is either situated according to given coordinates (x,y,z), or
setting the relative target_index of the component to focus at (next is +1).
This target position will be set to its AT position. When targeting to centered
components, such as spheres or cylinders, define an Arm component where to focus at.

Example: Res_sample(thickness=0.001,radius=0.02,yheight=0.4,focus_r=0.05, E0=14.6,dE=2, target_x=0, target_y=0, target_z=1)
\end{lstlisting}

\subsection*{Input parameters}
Parameters in \textbf{boldface} are required; the others are optional.

\begin{longtable}{p{0.22\textwidth}p{0.12\textwidth}p{0.46\textwidth}p{0.14\textwidth}}
\toprule
\textbf{Name} & \textbf{Unit} & \textbf{Description} & \textbf{Default} \\
\midrule
\endhead
thickness & m & Thickness of hollow cylinder in (x,z) plane & 0 \\
radius & m & Outer radius of hollow cylinder & 0.01 \\
focus\_r & m & Radius of sphere containing target. & 0.05 \\
E0 & meV & Center of scattered energy range & 14 \\
dE & meV & half width of scattered energy range & 2 \\
target\_x & m & X-position of target to focus at [m] & 0 \\
target\_y & m & Y-position of target to focus at & 0 \\
target\_z & m & Z-position of target to focus at [m] & .5 \\
focus\_xw & m & horiz. dimension of a rectangular area & 0 \\
focus\_yh & m & vert. dimension of a rectangular area & 0 \\
focus\_aw & deg & horiz. angular dimension of a rectangular area & 0 \\
focus\_ah & deg & vert. angular dimension of a rectangular area & 0 \\
xwidth & m & horiz. dimension of sample, as a width & 0 \\
yheight & m & vert. dimension of sample, as a height & 0.05 \\
zdepth & m & depth of sample & 0 \\
target\_index & 1 & relative index of component to focus at, e.g. next is +1 & 0 \\
\bottomrule
\end{longtable}

\subsection*{Links}
\begin{itemize}
  \item \href{run:/home/willend/willend-McCode/mcstas-comps/samples/Res_sample.comp}{Source code} for \texttt{Res\_sample.comp}.
\end{itemize}
\IfFileExists{Res_sample_static.tex}{\input{Res_sample_static.tex}}{}